Higher-Order unification for free!

### 2024-07-29 paper/paper_for_taps/source/PPDP2024-1.tex
new version (seems accepted by taps)
change dates 09-11 -> 10-11

\usepackage[newfloat]{minted}
\usepackage{xspace}
\usepackage{cleveref}
\usepackage{calc}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{intcalc}
\usepackage{nameref}

@@

\setcopyright{acmlicensed}  %
\copyrightyear{2024}
\acmYear{2024}
\setcopyright{rightsretained}
\acmConference[PPDP 2024]{26th International Symposium on Principles and Practice of Declarative Programming}{September 09--11, 2024}{Milano, Italy}
\acmBooktitle{26th International Symposium on Principles and Practice of Declarative Programming (PPDP 2024), September 09--11, 2024, Milano, Italy}
\acmPrice{}
\acmDOI{10.1145/3678232.3678233}
\acmISBN{979-8-4007-0969-2/24/09}

>>>>

\usepackage[newfloat,frozencache]{minted}
\usepackage{xspace}
\usepackage{cleveref}
\usepackage{calc}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{intcalc}
\usepackage{nameref}

@@

\setcopyright{acmlicensed}  %
\copyrightyear{2024}
\acmYear{2024}
\setcopyright{rightsretained}
\acmConference[PPDP 2024]{26th International Symposium on Principles and Practice of Declarative Programming}{September 10--11, 2024}{Milano, Italy}
\acmBooktitle{26th International Symposium on Principles and Practice of Declarative Programming (PPDP 2024), September 10--11, 2024, Milano, Italy}
\acmPrice{}
\acmDOI{10.1145/3678232.3678233}
\acmISBN{979-8-4007-0969-2/24/09}
